---
title: "Functions testing"
author: "AMCalejandro"
date: "15/10/2021"
output: html_document
---

```{r setup, include=FALSE}
library(here)

knitr::opts_chunk$set(echo = TRUE)
```


```{r}
cat("Markdown absolute path", getwd() )
cat("Top level project folder", here::here() )
```

# Description

This is the markdown in which I test out all the developed functions under the R directory.
Each section belongs to a different function


# Extraction

Extracting the middle character given a string, an dealing with even and odd characters


TO IMPROVE. ALLOW a list of characters as input. Retrieve the a dictionary having the character as key, and the mid char as the key value


```{r}
source(here::here("R", "extraction.R"))

string_even = "abcd"
strin_odd = "abcde"

extraction(string_even)
extraction(strin_odd)

# With this function, we can easily apply the strategy over a list "lapply"
vector_test = c("abcd", "abcde")
list_test = list("abcd", "abcde")
lapply(list_test, extraction)
lapply(vector_test,extraction)


# Errr testing

null_string = ""
extraction(null_string)


```
```{r}
source(here::here("R", "REGEX.R"))

data_words = stringr::words

# Words ending with "ed"
ed_ending(data_words)

#Words ending with either ise or ing
ingIse_ending(data_words)

```
```{r}
# Rpetitions

source(here::here("R", "REGEX.R"))

data_words = stringr::words

# Starts with three consonants
consonant_starter(data_words)

# Have three or more vowels in a row.
vowels_finder(data_words)
vowels_finder(data_words, capital = "upper")

# vowel-consonant finder
vc_finder(data_words)

```

